Self-tunable approximated explicit MPC: Heat exchanger implementation and analysys

### 2023-02-02 paper/elsarticle/main.tex
Paper: Introduction: initial part

	TODO: Vyhnut sa pouzivaniu "we", "our",...

	TODO: dopisat zaciatok uvodu o vymennikoch tepla, ladeni regulatorov vseobecne, gain-scheduling atd (neskor je pokryte MPC, MPC riadenie vymennikov tepla, eMPC, tunable eMPC a self-tunable)

@@

>>>>

%	TODO: Vyhnut sa pouzivaniu "we", "our",...
%	
%	TODO: dopisat zaciatok uvodu o vymennikoch tepla, ladeni regulatorov vseobecne, gain-scheduling atd (neskor je pokryte MPC, MPC riadenie vymennikov tepla, eMPC, tunable eMPC a self-tunable)

@@

	The current crisis of energy resources emphasizes the long-term goal of achieving sustainable industrial production and optimal energy utilization. Moreover, minimizing the energy utilization directly reduces the corresponding CO$_{2}$ emissions. Therefore, sustainable industrial production is focused on the wide implementation of advanced control methods~\cite{MN20}.

	The heat exchangers in their numerous variants integrated into the many industrial plants represent energy-demanding plants. From the control viewpoint, the controller design taking into account the nonlinear and asymmetric behaviour of the heat exchangers is a challenging task, see~\cite{RL20}. Although the conventional and widely-used PID controllers are robust and easy to tune, their control performance may not be sufficient when comes to energy savings. Various extensions built above the well-tuned PID controller were developed to compensate for the non-linear and asymmetric behaviour, often affected by the additional impact of the uncertain parameters originated e.g., in the fouling~\cite{MT19}. Such widely-used control strategies include, e.g., the robust control~\cite{DO15,WY18}, the gain-scheduling, multi-zone control, see~\cite{MF08,Liptak}, and references therein.
